Implementation of Concurrent Hash Tables in Java

### 2022-03-25 paper.tex
Manually Merging test-latex

@@

\begin{thebibliography}{00}
\bibitem{b1} R. Sedgewick and K. Wayne. "Hash Tables" princeton.edu \\https://algs4.cs.princeton.edu/34hash/ (accessed Mar. 13, 2022)
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\end{document}

>>>>

\subsection{What is Concurrency?}
Now given what a hash table is, this paper will look at what exactly it means for a computer program to be concurrent. Concurreny means that multiple computations
will be occuring at the same time. This has become increasing more important, with the clock speed of processors no longer increasing, it results in 
manufacturers adding more cores to chips, meaning splitting up computation among those chips is the only way to make it faster. Concurrent programming
has two common models: shared memory models and message passing models. This paper will only look at shared memory models as the implementation for
a concurrent hash table will utilize a shared memory model. A shared memory model works by having concurrent processors read and write objects into the
memory that they share [3].

@@

\section{Appendix}

\begin{thebibliography}{00}
\bibitem{b1} R. Sedgewick and K. Wayne. "Hash Tables." princeton.edu. \\https://algs4.cs.princeton.edu/34hash/ (accessed Mar. 13, 2022).
\bibitem{b2} S. Mitra. "Hashing." utexas.edu. https://www.cs.utexas.edu/~mitra/\\csSpring2017/cs313/lectures/hash.html (accessed Mar. 13, 2022).
\bibitem{b3} S. Amarasinghe, A. Chlipala, S. Devadas, M. Ernst, M. Goldman, J. Guttag, D. Jackson, R. Miller, M. Rinard, and A. Solar-Lezama. "Reading 17: Concurrency"
mit.edu. https://web.mit.edu/6.005/\\www/fa14/classes/17-concurrency/ (accessed Mar. 14, 2022).
\end{thebibliography}
\end{document}
